Canonical rings of rational divisors on projective space and Hirzebruch surfaces

### 2015-07-16 surfaces-write-up/surface-write-up.tex
ref fixes

\begin{rem}
\label{rem:proj-one-point-ind}
Note that the method of proof for Theorem ~\ref{thm:proj-one-point}
can be immediately generalized to work inductively. If $D = D' + H$
for some hyperplane $H$, then we can use the proof above to show
the canonical ring $R_D$ is generated over $R_D'$ by the same
generators and with the same relations given in Theorem
~\ref{thm:proj-one-points}.
\end{rem}

@@

\begin{proof}
First, we apply Remark ~\ref{rem:proj-veronese} to reduce the
problem to letting each $H_i$ be a hyperplane of $\bp^m$.
Then, the proof follows from applying Remark
~\ref{rem:proj-one-point-ind} inductively on a one-hyperplane case
from Theorem ~\ref{them:proj-one-point}.
\end{proof}

>>>>

\begin{rem}
\label{rem:proj-one-point-ind}
Note that the method of proof for Theorem ~\ref{thm:proj-one-point}
can be immediately generalized to work inductively. If $D = D' + H$
for some hyperplane $H$, then we can use the proof above to show
the canonical ring $R_D$ is generated over $R_D'$ by the same
generators and with the same relations given in Theorem
~\ref{thm:proj-one-point}.
\end{rem}

@@

\begin{proof}
First, we apply Remark ~\ref{rem:proj-veronese} to reduce the
problem to letting each $H_i$ be a hyperplane of $\bp^m$.
Then, the proof follows from applying Remark
~\ref{rem:proj-one-point-ind} inductively on a one-hyperplane case
from Theorem ~\ref{thm:proj-one-point}.
\end{proof}
